---
title: "qPCR_Report"
author: "Nicole M"
date: "9/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, include = TRUE)
```

## qPCR Data Analysis

- Different result spreadsheets for analysis with averages of the ct values for each sample for each gene
- Ref-finder determines most stable genes using four methods and shows the comprehensive results
- Code calculates efficiencies of replication for each gene relative to the standard curve ct values
- Then efficiencies are used to determine the relative concentrations based on the reference genes as the baseline and the calibrators to be able to compare between groups
```{r}
cal_run1 <- calData(nrmData(data=run1_CT,
                         r=3, #triplets of aliquots
                         E=Ef, #efficiency factors which are logarithmic (2.0 is 100%)
                         Eerror=c(0.02,0.02,0.02,0.02,0.02,0.02), #errors for each gene
                         nSpl=21, #amount of samples
                         nbRef=2, #2 reference genes
                         Refposcol=(1:2), #position of reference genes
                         nCTL=5, #which first samples are control (this has no control yet)
                         CF=c(1,1,1,1,1,1), # control factor for each gene
                         CalPos=21, # position of calibrator
                         trace=FALSE,
                         geo=TRUE,
                         na.rm=TRUE)[[3]]) #remove NA values (empty cells)
cal_run1
```




